---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ContainR

<!-- badges: start -->
<!-- badges: end -->

The goal of ContainR is to enable easier container development for computational reproducibility. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
# library(tidyverse)
# 
# data_rocker_table <- utils::data("data_rocker_table")
# 
# data_rocker_table %>% 
#   gt::gt() %>% 
#   gtExtras::gt_theme_538()
```


There are similar packages available such as [dockr](https://github.com/smaakage85/dockr) or [devindocker](https://github.com/ThinkR-open/devindocker) which provide various levels of functionality. We also recommend checking these out to see if these suit your requirements. 

## Installation

You can install the development version of ContainR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("psychtek/ContainR")
```
