---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ContainR
**Work in progress**
<!-- badges: start -->
<!-- badges: end -->

A set of functions that I found handy during development of the repliCATS pipeline. The goal of ContainR is to enable easier container development for computational reproducibility. It is currently a work in progess and welcome any issues and comments. 

At its core a user can run a command `docker_run()` which will launch the `rocker/rstudio:latest` stack into a Docker container, port **local config** and **environment** settings into the container and activate the Rstudio project. Wrappers for the basic Docker commands allow for ease of starting and stopping the container. 

Included images of the [rocker-versioned](https://github.com/rocker-org/rocker-versioned2) stacks can be found by exploring the `data_rocker_table` inside the package. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(ContainR)

data_rocker_table
```


## Installation

You can install the development version of `ContainR` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("psychtek/ContainR")
```

### Docker Check 
Check if Docker is installed on the system or installed for [OSX](https://docs.docker.com/desktop/install/mac-install/), [Windows](https://docs.docker.com/desktop/install/windows-install/) or [Linux](https://docs.docker.com/engine/install/). 

```r
docker_check()
```

## Create a Dockerfile 

The benefit of this package was to allow a researcher ease of developing a container without deep dive learning about Docker commands. The `docker_file()` function is an attempt to make it easier to create a `Dockerfile` by allowing the user to: 

1) choose the rocker base image, 

2) choose to install either the local `loaded`, `installed` or `none` packages, 

3) choose to included python. 

```r
docker_file(dockerfile = "inst/dockerfiles/Dockerfile",
                   which_pkgs = "none",
                   name = "rstudio",
                   tag = "latest",
                   include_python = TRUE)

```

The benefit of this functionality gives the user the choice to build a container image and only include
packages that are loaded at the time of development. The install scripts also skip any packages already installed on the base Rocker image. 

The `docker_build()` function will then read the newly created `Dockerfile` and build the image based on the previous user requirements. 

```r
docker_build(dockerfile =  "inst/dockerfiles/Dockerfile", name = "projectname")
```

Finally,`docker_run()` is can then be used (with the user supplied Docker image) to launch a Rstudio container in the browser activating the current working project. 

```r
rocker_run()

```

There are similar packages available such as [dockr](https://github.com/smaakage85/dockr) or [devindocker](https://github.com/ThinkR-open/devindocker) which provide various levels of functionality. We also recommend checking these out to see if these address your requirements. 
